Sampling Bayesian probabilities given only sampled priors

### 2024-12-17 main.tex
A few typos fixed in latex and a whole new version of python routine.
Add Modes class to code and put new derivation into latex file

\newcommand{\ie}{\textit{i.e.}}
\newcommand{\eg}{\textit{e.g.}}
\newcommand{\E}{\mathrm{E}}
\newcommand{\eqq}[1]{Equation~(\ref{#1})}
\newcommand\gary[1]{{\color{red} \{\textbf{GMB}: #1\}}}
%\tabletypesize{\footnotesize}
\newcommand{\vecc}{\ensuremath{\mathbf{c}}}
\newcommand{\vecq}{\ensuremath{\mathbf{q}}}
\newcommand{\vecn}{\ensuremath{\mathbf{n}}}
\newcommand{\vecu}{\ensuremath{\mathbf{u}}}
\newcommand{\hatc}{\ensuremath{\hat{\mathbf{c}}}}
\newcommand{\vecP}{\ensuremath{\mathbf{P}}}
\newcommand{\covm}{C}
\newcommand{\matA}{\ensuremath{A}}
\newcommand{\matD}{D}
\newcommand{\matU}{U}
\newcommand{\matV}{V}
\newcommand{\matW}{W}
\newcommand{\proj}{P}  % Projection matrix
\newcommand{\jac}{J}   % Jacobian
\newcommand{\ident}{I}  % identity
\newcommand{\DD}{\Delta_D}
\newcommand{\likeli}{\mathcal{L}}
\newcommand{\trace}{\text{Tr}}
\begin{document}

@@

We describe here an approach that is algebraically similar to that of \citet{hans}, but does not require 2nd condition of Gaussianity for the nuisance prior, and is somewhat more robust to non-linearities in the model that violate the 3rd condition.  Our approach is to seek a linear compression of \vecn\ into a lower-dimensional set of parameters \vecu\ that project away variations in \vecn\ that do not influence the likelihood $\likeli.$  Standard density estimators can then be applied to the \vecu\ values implied by the known \vecn\ samples to yield a prior $p(\vecu)$ that can be used for the MC chain of the cosmological posterior.  The model \hatc, and hence $\likeli,$ will be continuous over this low-dimensional \vecu\ space, and marginalization over \vecu\ will yield posterior probabilities very close to marginalization over the original \vecn.

\section{Derivation}\label{sec:deriv}
We assume that we do have a multivariate normal likelihood for the
observables \vecc\, with the mean being some model
$\hatc(\vecq,\vecn)$ and a fixed covariance matrix $\covm_c.$ In this
section we will assume that the \vecn\ vectors have been shifted by
the mean $\vecn_0 \equiv \left\langle \vecn_\alpha \right\rangle$ so
that their mean is zero.
We seek some function $\hat{\vecn}(\vecu)$ of a lower-dimensional vector \vecu\ which can be substituted for \vecn\ and yield nearly the same likelihood function for any \vecn\ in the domain spanned by the samples $\vecn_\alpha,\; \alpha\in 1\ldots N_\alpha,$ that we are provided.  This means we want a map $\vecn_\alpha\rightarrow \vecu_\alpha$ and a function $\hat{\vecn}(\vecu)$ which minimize the error in log-likelihood
\begin{equation} -2 \left\langle \log \likeli(\vecc | \vecq,\vecn) - \log \likeli(\vecc | \vecq,\hat{\vecn}(\vecu)) \right\rangle =
  \left\langle \Delta\chi^2 \right\rangle \approx \frac{1}{N_\alpha} \sum_\alpha
                                            \left[ \hatc(\vecq,\vecn_\alpha) - \hatc(\vecq,\hat{\vecn}(\vecu_\alpha)) \right]^T
                                            \covm_c^{-1}
                                            \left[ \hatc(\vecq,\vecn_\alpha) - \hatc(\vecq,\hat{\vecn}(\vecu_\alpha)) \right].
                                          \end{equation}

If we next define the Jacobian matrix
\begin{equation}
  \jac \equiv \left.\frac{\partial\hatc}{\partial\vecn}\right|_{\vecq_0, \vecn_0}
\label{eq:jacobian}
\end{equation}
and assume that a first-order Taylor expansion about the nominal values is valid across the domain of interest, then we obtain
\begin{equation}
  \left\langle \Delta\chi^2 \right\rangle \approx \frac{1}{N_\alpha} \sum_\alpha
  \left[ \vecn_\alpha - \hat{\vecn}(u_\alpha)\right]^T \jac^T \covm_c^{-1} \jac
  \left[ \vecn_\alpha - \hat{\vecn}(u_\alpha)\right].
  \label{eq:linearized}
\end{equation}
We ask what is the optimal \emph{linear} model $\hat{\vecn} = \matU \cdot \vecu$ to use.
It is useful to define the matrix \matD, its eigensystem
$(\matV_D,\Lambda_D),$  \ and its ``square root'' $\DD$ by
\begin{equation}
   \matD \equiv \jac^T \covm_c^{-1} \jac =  \matV_D \Lambda_D
   \matV_D^T = \left(\matV_D \Lambda_D^{1/2}\right)
   \left(\Lambda_D^{1/2}\matV_D^T \right) = \DD^T \DD.
 \end{equation}
Since \matD\ is non-negative and symmetric, $\DD$ will exist and be
real-valued with non-negative singular values.
If \vecn\ has $N$ elements, and we want to compress the representation
to a vector \vecu\ with $M$ elements, we will use the $M\times N$ projection
matrix $\proj_M$ whose elements are
\begin{equation}
  \left(\proj_M\right)_{ij} \equiv
\begin{cases}
                                            1,  &  i=j\le M \\
                                            0,  & \text{otherwise.}
\end{cases}
\end{equation}
such that $\proj_M \proj_M^T=\ident_M,$ the $M\times M$ identity
matrix. We will assume that \matU\ satisfies
\begin{equation}
  \DD \matU = \matV_U \proj_M^T
\label{eq:vupm}
\end{equation}
for some unitary matrix $\matV_U$.  We can do this because, for any $\matU$, we have the
singular-value decomposition $\DD \matU = \matV_U P_M^T \Lambda_U
W_U^T,$ where $\Lambda_U$ is diagonal, $W_U$ is unitary, and both are
$M\times M$.  We can always absorb these last two factors into the \vecu\ values
to conserve the values of $\hat{\vecn} = \matU \vecu$ while making
\eqq{eq:vupm} hold.

With these definitions and a choice of \matU, the $\chi^2$ error and the values of $\vecu_\alpha$ that minimize it become
\begin{align}
  \left\langle \Delta\chi^2 \right\rangle & \approx \frac{1}{N_\alpha} \sum_\alpha
                                            \left[ \vecn_\alpha - \matU \vecu_\alpha\right]^T \matD^{-1}
                                            \left[ \vecn_\alpha - \matU \vecu_\alpha\right] \\
  \Rightarrow \quad \vecu_{\alpha,\text{min}} & = \left[ \matD -
                                                \matD\matU\left(\matU^{T}\matD\matU\right)^{-1}
                                                \matU^T\matD\right]\vecn_\alpha  \\
                                          & = \proj_M \matV_U^T \DD \vecn_\alpha.
\end{align}                                            
Defining the covariance matrix of the samples $\vecn_\alpha$ as
$\covm_n=\left\langle \vecn_\alpha \vecn^T_\alpha \right\rangle,$ and
plugging the last line back into the first,  gives us the quantity we
want to minimize by selecting \matU\ properly:
\begin{align}
  \left\langle \Delta \chi^2 \right\rangle 
  & = \trace\left[\covm_n\matD
    - \covm_n \DD^T \matV_U \proj_M^T \proj_M \matV_U^T \DD \right], \\
 & = \trace\left[\matV_A \Lambda_A \matV_A^T 
    - \Lambda_A  \matV_A^T \matV_U \proj_M^T \proj_M \matV_U^T
   \matV_A\right], \\
  & = \sum_{i=1}^N \lambda^A_i \left[ 1 - \sum_{j=1}^M (\matV^T_A
    \matV_U)^2_{ij}\right], \label{eq:dchi2} \\
  \text{with} \quad \matA & \equiv \DD \covm_c \DD^T = \matV_A \Lambda_A \matV_A^T.
\end{align}
The last line defines a new symmetric, non-negative matrix \matA\ that
has eigenvectors $\matV_A$ and positive eigenvalues $\Lambda_A=\text{Diag}(\lambda^A_1,
\lambda^A_2, \ldots, \lambda^A_N).$ We assume the eigenvalues are
placed into decreasing order.

The minimization of $\left\langle \chi^2 \right\rangle$ thus requires
choosing $\matV_U,$ to minimize \eqq{eq:dchi2}, then retrieving \matU\
from \eqq{eq:vupm}.  Since $\matV_A^T\matV_U$ is a unitary matrix,
each term in brackets must be non-negative and $\le 1,$ and their total must equal
$N-M$.  The optimal case would be to have the bracketed term be zero
for $i\le M$, and be unity when multiplying the smaller $\lambda^A_i$
at $i>M.$  This occurs when $\matV_U=\matV_A,$ which is therefore our
optimal compression in terms of reproducing the likelihood of the
data.

The desired linear compression of \vecn\ therefore has the following properties:
\begin{itemize}
\item The mean error in $2\log \likeli$ is
  \begin{equation}
    \left\langle \Delta\chi^2 \right \rangle = \sum_{i=M+1}^N
    \lambda^A_i,
  \end{equation}
  and we will want to choose the dimension $M$ of the compression to
  keep this quantity, the observable effect of the parts of \vecn\ that we 
  project away,  below unity.
  Note that the $\lambda^A_i$ values are determined by a combination of
  the covariance matrix of the samples of \vecn, along with the Jacobian
  matrix and the covariance $\covm_c$ of the observables, letting us
  know the measurement significance of each mode of variation of \vecn.

  \item The \matU\ matrix containing the $M$ basis vectors for
    reconstructing \vecn\ is
    \begin{equation}
      \matU = \DD^{-1} \matV_A \proj_M^T = \matV_D \Lambda_D^{-1/2}  \matV_A \proj_M^T.
    \end{equation}
    In inverting the (non-negative, diagonal) matrix $\Lambda_D^{1/2},$ one should null the
    inverses of elements that are $\lesssim 10^{-3}$ of the largest
    element, to avoid adding large fluctuations to \matU\ that address
    noise or roundoff-error terms that contribute negligibly to $\chi^2.$

  \item The compressed $\vecu_\alpha$ for a chosen sample of \vecn\ is
    \begin{equation}
      \vecu_\alpha = \proj_M \matV_A^T \DD \vecn_\alpha = \proj_M
      \matV_A^T \Lambda_D^{1/2} \matV_D^T \vecn_\alpha,
    \end{equation}
    and the covariance matrix of the compressed samples is
    \begin{equation}
      \covm_u = \left\langle \vecu \vecu^T \right\rangle = \proj_M
      \matV_A^T \DD \covm_n \DD^T \matV_A \proj_M^T = \text{Diag}(\lambda^A_1,
      \lambda^A_2, \ldots \lambda^A_M).
    \end{equation}
The components of the compressed \vecu\ coefficients are therefore
uncorrelated.  Component $u_i$ has a variance
$\lambda^A_i,$ which is also equal to the reduction in $\left\langle
  \Delta \chi^2 \right\rangle$ that we will accrue if we include basis
vector $\mathbf{U}_i$ into our linear reconstruction of \vecn.
\end{itemize}
The compression thus consists of choosing the desired number of rows
of the matrix $ \matV_A^T \Lambda_D^{1/2} \matV_D^T$, and the modes
are the corresponding columns of this matrix's inverse, with each
included mode reducing the mean compression error in mean $\chi^2$ by $\lambda^A_i.$

Upon executing the compression $\{\vecn_\alpha\} \rightarrow
\{\vecu_\alpha\},$ we may find the distribution of the samples to be
consistent with a multivariate normal---which will have the diagonal covariance
matrix $\covm_u,$ and statistical independence for the elements of
\vecu.
There is,however,  no \textit{a prior} reason that
this must be the case.  We can use any density estimator over
$\{\vecu_\alpha\}$ to define a continuous $p(\vecu)$ for a Markov
chain running over the $(\vecq,\vecu)$ space.  This is the principle
advantage of our method over the single-step covariance-inflation
method of \citet{hans}.

Even if the \vecu\ prior is well approximated as multivariate normal,
there are practical advantages of compressing the nuisance 
variables and retaining them in the cosmological Markov chain rather
than using the covariance-inflation method for analytic
marginalization.  One can, for example, examine the posterior
distributions of \vecu\ and see if they are at the edges of the prior,
which would potentially indicate an inconsistency between the data and
the prior.

>>>>

\newcommand{\ie}{\textit{i.e.}}
\newcommand{\eg}{\textit{e.g.}}
\newcommand{\E}{\mathrm{E}}
\newcommand{\eqq}[1]{Equation~(\ref{#1})}
\newcommand\gary[1]{{\color{red} \{\textbf{GMB}: #1\}}}
%\tabletypesize{\footnotesize}
\newcommand{\vecc}{\ensuremath{\mathbf{c}}}
\newcommand{\vecq}{\ensuremath{\mathbf{q}}}
\newcommand{\vecn}{\ensuremath{\mathbf{n}}}
\newcommand{\vecu}{\ensuremath{\mathbf{u}}}
\newcommand{\vecv}{\ensuremath{\mathbf{v}}}
\newcommand{\hatc}{\ensuremath{\hat{\mathbf{c}}}}
\newcommand{\vecP}{\ensuremath{\mathbf{P}}}
\newcommand{\covm}{C}
\newcommand{\matA}{\ensuremath{A}}
\newcommand{\matD}{D}
\newcommand{\matE}{E}
\newcommand{\matF}{F}
\newcommand{\matG}{G}
\newcommand{\matI}{I}
\newcommand{\matT}{T}
\newcommand{\matX}{X}
\newcommand{\matY}{Y}
\newcommand{\matV}{V}
\newcommand{\matLam}{\Lambda}
\newcommand{\proj}{P}  % Projection matrix
\newcommand{\jac}{J}   % Jacobian
\newcommand{\ident}{I}  % identity
\newcommand{\DD}{\Delta_D}
\newcommand{\likeli}{\mathcal{L}}
\newcommand{\trace}{\text{Tr}}
\begin{document}

@@

We describe here an approach that is algebraically similar to that of \citet{hans}, but does not require 2nd condition of Gaussianity for the nuisance prior.  Our approach is to seek a linear compression of \vecn\ into a lower-dimensional set of parameters \vecu\ that project away variations in \vecn\ that do not influence the likelihood $\likeli.$  Standard density estimators can then be applied to the \vecu\ values implied by the known \vecn\ samples to yield a prior $p(\vecu)$ that can be used for the MC chain of the cosmological posterior.  The model \hatc, and hence $\likeli,$ will be continuous over this low-dimensional \vecu\ space, and marginalization over \vecu\ will yield posterior probabilities very close to marginalization over the original \vecn.

\section{Derivation}\label{sec:deriv}
We assume that we do have a multivariate normal likelihood for the
observables \vecc\, with the mean being some model
$\hatc(\vecq,\vecn)$ and a fixed covariance matrix $\covm_c.$ In this
section we will assume that the \vecn\ vectors have been shifted by
the mean $\vecn_0 \equiv \left\langle \vecn_\alpha \right\rangle$ so
that their mean is zero.
We seek some function $\hat{\vecn}(\vecu)$ of a lower-dimensional
vector \vecu\ which can be substituted for \vecn\ and yield nearly the
same likelihood function for any \vecn\ in the domain spanned by the
samples $\vecn_\alpha,\; \alpha\in 1\ldots N_\alpha,$ that we are
provided.  This means we want a map $\vecn_\alpha\rightarrow
\vecu_\alpha \rightarrow \hat{\vecn}_\alpha$ such that replacing $\vecn$ with
$\hat\vecn$ alters the cosmological inference by much less than the
other uncertainties.  We will implement this by minimizing the
distance in the space $\vecc$ between the
model generated by $\vecn$ and that by $\hat\vecn$, using the
observations' covariance matrix $\covm_c$ as a metric for the
distance.  This is equivalent to the $\chi^2$ of the difference
between the original and compressed models for the data:
\begin{equation} \left\langle \chi^2 \right\rangle
=  \frac{1}{N_\alpha} \sum_\alpha
                                            \left[ \hatc(\vecq,\vecn_\alpha) - \hatc(\vecq,\hat{\vecn}_\alpha) \right]^T
                                            \covm_c^{-1}
                                            \left[ \hatc(\vecq,\vecn_\alpha) - \hatc(\vecq,\hat{\vecn}\alpha) \right].
\label{eq:chisq}
\end{equation}
If the data are in fact drawn from the model $\hatc(\vecq,\vecn)$ with
a Gaussian likelihood, then this is also the mean shift in $-2\log\likeli$
from the compression.  It is \emph{not}, however, equal to the mean
shift of the overall log of the posterior in
\eqq{eq:posterior}---$\left\langle\chi^2\right\rangle$ is serving as a
proxy for this.

We next assume that the compression is linear, $\hat\vecn=\matX\vecn,$
for some matrix that is idempotent ($\matX\matX = \matX$).  If this is
true, then the contribution to \eqq{eq:chisq} at lowest order in
$\vecn-\hat\vecn$ is
\begin{equation}
  \left\langle \chi^2 \right\rangle = \frac{1}{N_\alpha} \sum_\alpha
  \left[ (\matI-\matX)\vecn_\alpha\right]^T \matF  \left[ (\matI-\matX)\vecn_\alpha\right]
  \label{eq:linearized}
\end{equation}
where we use the Jacobian matrix of the model $\hatc$ to define
\begin{equation}
  \matF \equiv
  \left[\frac{\partial\hatc}{\partial\vecn}\right]_{\vecq_0, \vecn_0}
  \covm_c^{-1} \left[\frac{\partial\hatc}{\partial\vecn}\right]_{\vecq_0,
    \vecn_0}^T.
\label{eq:fisher}
\end{equation}
This quantity is also the Fisher matrix over $\vecn$ giving the information
provided by the observations $\vecc.$  In many cases this matrix will be
rank-deficient and/or poorly conditioned, since the observables are not
likely to be very informative on $\vecn$---if they were, we might not be
concerned with establishing a prior on $\vecn$ to begin with.  We will
not, however, require its inverse.

Since $\matX$ is idempotent, we can write
\begin{align}
  \matX & = V_X \proj_M V_X^T, \\
  \matY \equiv \matI-\matX & = V_X \proj_{-M} V_X^T,
\end{align}
where $V_X$ is unitary and the projection matrix $\proj_M$ is defined as
\begin{equation}
  \left(\proj_M\right)_{ij} \equiv
\begin{cases}
                                            1,  &  i=j\le M \\
                                            0,  & \text{otherwise}
\end{cases}
\end{equation}
and $\proj_{-M}=\matI-\proj_M.$  For a chosen rank $M$ of the
transformation matrix $X$, our task becomes to identify the
eigenvectors $V_X$ that minimize
\begin{align}
  \left\langle \chi^2\right\rangle & = \frac{1}{N_\alpha} \sum_\alpha
  \left[ \matY \vecn_\alpha\right]^T \matF  \left[\matY
                                     \vecn_\alpha\right] \\
       & = \trace \left[ \covm_n V_X \proj_{-M} V_X^T \matF V_X
         \proj_{-M} V_X^T \right].
\end{align}
This optimization is easier if we transform first the systematic variables to
$\vecn^\prime =\matT\vecn$ such that $\covm_{n^\prime}=\matI$, \ie\
make the elements of $\vecn$ uncorrelated and unit-variance.  This
is accomplished by finding the eigensystem $\covm_n=\matV_n \matLam_n
\matV_n^T$ and setting $\matT = \matLam_n^{-1/2} \matV_n^T$.  With
this transformation, we are now seeking a different unitary matrix
$\matV_{X^\prime}$ that minimizes
\begin{align}
  \left\langle \chi^2\right\rangle & = \trace \left[ \matI
    V_{X^\prime} \proj_{-M} V_{X^\prime}^T \left[ (T^{-1})^T \matF
      T^{-1} \right] V_{X^\prime} 
    \proj_{-M} V_{X^\prime}^T \right] \\
  & = \trace \left[ \proj_{-M} V_{X^\prime}^T \matV_G \matLam_G \matV_G^T
    V_{X^\prime} \proj_{-M} \right],
  \label{eq:mintr}\\
  \matG \equiv \left(T^{-1}\right)^T \matF   T^{-1} & = \matLam_n^{1/2} \matV_n^T
  \matF \matV_n \matLam_n^{1/2} = \matV_G \matLam_G \matV_G^T.
  \label{eq:defG}
\end{align}
The last line defines a transformed Fisher matrix $\matG$ and its
(non-negative) eigensystem.  Examination of \eqq{eq:mintr} reveals that this quantity
is minimized if the elements of the unitary matrices satisfy
$\matV_{X^\prime}^T \matV_G = \matI \; \Rightarrow \; \matV_{X^\prime} = \matV_G,$ and the eigensystem of $G$ is placed
in order of decreasing eigenvalue $\lambda^G_i.$ The
elements surviving the project functions yield
\begin{equation}
  \left\langle \chi^2\right\rangle = \sum_{i>M} \lambda_i^G.
  \label{eq:chiresid}
\end{equation}
In other words each eigenvalue of the matrix $\matG$ in \eqq{eq:defG}
gives the contribution to $\left\langle\chi^2\right\rangle$ of one
projection (mode) of $\vecn.$

Transforming the solution back into the space of $\vecn$ yields
\begin{align}
  \matX & = \matT^{-1} \matV_G \proj_M \matV_G^T \matT \\
   & = \left[ \matV_n^T \matLam_n^{1/2} \matV_G \proj_M \right] \left[
     \proj_M \matV_G^T \matLam_n^{-1/2} \matV_n^T \right] \\
\label{eq:DE}
        & \equiv \matD \matE.
\end{align}
We thus obtain our optimal encoding/compression using the nonzero rows of matrix
$\matE$ to give
\begin{equation}
  \vecu_\alpha = \matE \vecn_\alpha
  \label{eq:uu}
\end{equation}
and the decoding/reconstruction of the systematic variables as
\begin{equation}
  \hat\vecn_\alpha = \matD \vecu_\alpha.
  \label{eq:UU}
\end{equation}
One can confirm that this procedure yields a compressed representation
$\vecu$ such that $\covm_u = \matI_M,$ the $M$-dimensional
identity matrix.

The previous derivation ignores the possibility that $\covm_n$ is
singular or nearly so, such that taking $\matLam_n^{-1/2}$ in
\eqq{eq:DE} is not possible.  Indeed in our application, it is
\emph{required} that $\covm_n$ be singular, because we have a sum
normalization constraint on the initial $\vecn_\alpha$ values.  Any
such (nearly) zero element $j$ of $\matLam_n$ has a corresponding
eigenvector $\vecv_j$ of the $\vecn$ space which has zero amplitude
in all of the input samples $\vecn_\alpha,$ so that the $\vecn$ are
confined to a subspace---the reconstructed $\hat\vecn$ should also be.
The compressed
representations $\vecu_\alpha$ and reconstructed $\hat\vecn_\alpha$
should therefore be unaffected by the presence of any $\vecv_j$
component.  This can be accomplished in \eqq{eq:DE} by setting element
$j$ of $\matLam_n^{-1/2}$ to zero, as is typically done during
solutions of least-squares problems using singular value
decompositions.

In summary, the procedure for dimensional reduction is:
\begin{enumerate}
  \item Obtain the Fisher matrix $\matF$ of the system defined in
    \eqq{eq:fisher} using derivatives about the mean sample $\vecn_0,$
    plus the covariance matrix $\covm_n$ of the samples.
  \item From the eigensystem $(\matLam_n,\matV_n)$ of $C_n$, form the
    matrix $G$ defined in \eqq{eq:defG} and get its eigensystem
    $(\matLam_G,\matV_G).$  Place the eigenvalues in descending order.
  \item Choose the size $M$ of the compressed representation to be the
    minimum that keeps the $\left\langle\chi^2\right\rangle$ value in
    \eqq{eq:chiresid} below a chosen threshold, presumably $\ll 1.$
  \item The encoding matrix $E$ and decoding matrix $D$ are formed as
    in \eqq{eq:DE}, taking the inverse $\matLam_n^{-1/2}$ to be zero
    for any eigenvalues that are zero (or within roundoff errors).
  \item Compress all incoming (mean-subtracted) samples using \eqq{eq:uu}.  They will
    have unit covariance matrix and zero mean.
  \item Construct a continuous density estimator in $\vecu$ space that
    mimics the finite sample distribution.  If the distribution is
    normal, this becomes the multidimensional unit normal.  There
    is, however,  no \textit{a prior} reason that this must be the case,
    and something like a normalizing flow will be needed to
    approximate this lower-dimensional representation of the prior.
  \item Sample over $\vecu$ space in the Markov Chain that is sampling the
    posterior on the parameters of interest $\vecq,$ using \eqq{eq:UU}
    to transform each sample back into a $\hat\vecn$ vector.
  \end{enumerate}

The ability to accomodate non-Gaussian distributions of the
nuisance-parameter space is the principle
advantage of our method over the single-step covariance-inflation
method of \citet{hans}.
But even if the \vecu\ prior is well approximated as multivariate normal,
there are practical advantages of compressing the nuisance 
variables and retaining them in the cosmological Markov chain rather
than using the covariance-inflation method for analytic
marginalization.  One can, for example, examine the posterior
distributions of \vecu\ and see if they are at the edges of the prior,
which would potentially indicate an inconsistency between the data and
the prior.
